\cvsection{Education}
\begin{cventries}
  \cventry
    {Ph.D. in Gravitational Waves Astronomy}
    {University of Balearic Islands}
    {Palma, Spain}
    {2016 - 2020}
    {
      \begin{cvitems}
        \item {Thesis: \textit{Waveform Modelling of Binary Black Holes in the Advanced LIGO Era} }
        \item {\textit{Viva voice}: July 2020 -- Awarded: July 2020 -- Honours: \textit{cum laude}}
        \item {Supervisors: Prof. Sascha Husa, Prof. Alicia Sintes Olives}
      \end{cvitems}
    }\vspace{-10pt}
    
    \cventry
    {M.S. in Physics: Radiation, Nanotechnology, Particles and Astrophysics}
    {University of Granada}
    {Granada, Spain}
    {2015}
    {
      \begin{cvitems}
        \item {Average mark: 9.2/10}
        \item {Specialized in Particles and Astrophysics.}
        \item {Master thesis: \textit{Formulations of General Relativity as Gauge Theory}. Extensive manual tensorial calculations in curve geometries, including (Anti-)de Sitter spaces and different kinds of local transformations. Study if they allow the quantization of gravity.}
        \item{Supervisor: Prof. Bert Jansen}
      \end{cvitems}
    }\vspace{-10pt}
    
    \cventry
    {B.Sc. in Physics}
    {University of Granada}
    {Granada, Spain}
    {2010 - 2014}
    {
      \begin{cvitems}
        \item {Average mark: 9.1/10}
        \item {Bachelor thesis: \textit{Uncertainty Relations in Quantum Information.} Extensive review of the different existing formulations of the Heisenber principle by using other uncertainty measurements like the Shannon or Renyi entropies.}
        \item{Supervisor: Prof. Jesús Sánchez-Dehesa}
      \end{cvitems}
    }\vspace{-10pt}
    
\end{cventries}
