\cvsection{Publications}
\cvsubsection{Refereed}
\begin{cvpubs}
  \cvpub
    {
      \begin{cvetar}
       \item {H. Estellés, A. Ramos-Buades, S. Husa, \textbf{C. García-Quirós}, M. Colleoni, L. Haegel, and R. Jaume. ``Phenomenological time domain model for dominant quadrupole gravitational wave signal of coalescing binary black holes''. \textit{Physical Review D} 103, 124060, 2021. \url{https://doi.org/10.1103/PhysRevD.103.124060}}
       \item {G. Pratten, \textbf{C. García-Quirós}, M. Colleoni, A. Ramos-Buades, H. Estellés, M. Mateu-Lucena, R. Jaume, M. Haney, D. Keitel, J. E.Thompson, and S. Husa. ``Computationally efficient models for the dominant and subdominant harmonic modes of precessing binary black holes''. \textit{Physical Review D}, 103, 104056, 2021. \url{https://doi.org/10.1103/PhysRevD.103.104056}}
       \item {M. Colleoni, M. Mateu-Lucena, H. Estellés, \textbf{C. García-Quirós}, D. Keitel, G. Pratten, A. Ramos-Buades, and S. Husa. ``Towards the routine use of subdominant harmonics in gravitational-wave inference: Reanalysis of GW190412 with generation X waveform models''. \textit{Physical Review D} 103, 024029, 2021. \url{https://doi.org/10.1103/physrevd.103.024029}}
       \item {\textbf{C. García-Quirós}, S. Husa, M. Mateu-Lucena, and A. Borchers. ``Accelerating the evaluation of inspiral–merger–ringdown waveforms with adapted grids''. \textit{Classical and Quantum Gravity}, 38(1):015006, 2020. \url{https://doi.org/10.1088/1361-6382/abc36e}}
       \item{\textbf{C. García-Quirós}, M. Colleoni, S. Husa, H. Estellés, G. Pratten, A. Ramos-Buades, M. Mateu-Lucena, and R. Jaume. ``Multimode frequency-domain model for the gravitational wave signal from nonprecessing black-hole binaries.'' \textit{Physical Review D} 102 064002, 2020. \url{https://doi.org/10.1103/PhysRevD.102.064002}}
       \item {G. Pratten, S. Husa, \textbf{C. García-Quirós}, M. Colleoni, A. Ramos-Buades, H. Estellés, and R. Jaume. ``Setting the cornerstone for a family of models for gravitational waves from compact binaries: The dominant harmonic for nonprecessing quasicircular black holes''. \textit{Physical Review D} 102, 064001, 2020. \url{https://doi.org/10.1103/physrevd.102.064001}}
       \item {I. M. Romero-Shaw, et al. (\textbf{C. García-Quirós} position 29 of 59 authors). ``Bayesian inference for compact binary coalescences with bilby: validation and application to the first LIGO–Virgo gravitational-wave transient catalogue''. \textit{Monthly Notices of the Royal Astronomical Society}, Volume 499, Issue 3, Pages 3295–3319, 2020. \url{https://doi.org/10.1093/mnras/staa2850}}
       \item {A. Ramos-Buades, S. Husa, G. Pratten, H. Estellés, \textbf{C. García-Quirós}, M. Mateu-Lucena, M. Colleoni, and R. Jaume. ``First survey of spinning eccentric black hole mergers: Numerical relativity simulations, hybrid waveforms, and parameter estimation''. \textit{Physical Review D} 101, 083015, 2020. \url{https://doi.org/10.1103/PhysRevD.101.083015}}
       \item {L. London, S. Khan, E. Fauchon-Jones, \textbf{C. García}, M. Hannam, S. Husa, X. Jiménez-Forteza, C. Kalaghatgi, F. Ohme, and F. Pannarale. ``First Higher-Multipole Model of Gravitational Waves from Spinning and Coalescing Black-Hole Binaries''. \textit{Physical Review Letters} 120, 161102, 2018. \url{https://doi.org/10.1103/physrevlett.120.161102}}
       \item{As a member of the LIGO-Virgo collaboration I have been coauthor of more than 50 articles. A full list of refereed papers can be found at \url{https://www.scopus.com/authid/detail.uri?authorId=57196021724}}
      \end{cvetar}
    }
    
\end{cvpubs}\vspace{-10pt}

\cvsubsection{Unrefereed}
\begin{cvpubs}
  \cvpub
    {
      \begin{cvetar}
        \item {H. Estellés, S. Husa, M. Colleoni, M. Mateu-Lucena, M. de Lluc Planas, \textbf{C. García-Quirós}, D. Keitel, A. Ramos-Buades, A. K. Mehta, A. Buonanno, S. Ossokine. ``A detailed analysis of GW190521 with phenomenological waveform models'', 2021. \url{https://arxiv.org/abs/2105.06360}}
        \item {M. Mateu-Lucena, S. Husa, M. Colleoni, H. Estellés, \textbf{C. García-Quirós}, David Keitel, M. de Lluc Planas, A. Ramos-Buades. ``Adding harmonics to the interpretation of the black hole mergers of GWTC-1'', 2021. \url{https://arxiv.org/abs/2105.05960}}
        \item {H. Estellés, M. Colleoni, \textbf{C. García-Quirós}, S. Husa, D. Keitel, M. Mateu-Lucena, M. de Lluc Planas, A. Ramos-Buades. ``New twists in compact binary waveform modelling: a fast time domain model for precession'', 2021. \url{https://arxiv.org/abs/2105.05872}}
        \item {H. Estellés, S. Husa, M. Colleoni, D. Keitel, M. Mateu-Lucena, \textbf{C. García-Quirós}, A. Ramos-Buades, A. Borchers. ``Time domain phenomenological model of gravitational wave subdominant harmonics for quasi-circular non-precessing binary black hole coalescences'', 2021. \url{https://arxiv.org/abs/2012.11923}}
      \end{cvetar}
    }
\end{cvpubs}\vspace{-10pt}
